FoRTE baseline

### 2019-06-07 analysis/paper/paper.Rmd
First draft of text on submodels

In this study, we run a factorial experiment of ED2 with the following features enabled or disabled:
- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
    - For details, see Supplements S9 and S10 in [@longo_2019_ed1].
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation
    - V~cmax~(0) decline with shade tolerance is supported by classic ecological theory on succession [@bazzaz_1979_physiological]

>>>>

In this study, we ran a factorial combination of the following ED2 configurations: (1) two-stream vs. multiple-scatter canopy radiative transfer models; (2) infinite vs. finite crown area (a.k.a. complete vs. partial shading); and (3) static vs. light-plastic traits.

Both canopy radiative transfer models in ED2 resolve the full vertical radiation profile within a patch as a function of canopy structure (leaf and wood area indices, crown area, leaf angle distribution) and incident solar radiation.
The two models differ in the mathematical approximations of the underlying differential radiative transfer equations.

- Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
    - For details, see Supplements S9 and S10 in [@longo_2019_ed1].
- Multiple scatter model
    - Based on @zhao_2005_multiple

The crown area submodel in ED2 determines the nature of competition for light between cohorts.
In the default configuration ("infinite crown area", or "complete shading"), the leaf area of a cohort is distributed across the entire horizontal area of a patch.
This means that taller cohorts always receive more incoming radiation than shorter cohorts, even when the height difference is small.
Put another way, this means that there is no horizontal competition, only vertical.
This has been shown to excessively suppress competition from sub-dominant individuals and result in unrealistically homogeneous canopies [@fisher_2015_taking].
In the alternate configuration ("finite crown area", or "partial shading"), canopies take up only a fraction of the available horizontal area, meaning that multiple cohorts of similar height can receive the same level of light.
The horizontal area of crowns is determined by allometric equations from @dietze_2008_changing.

The third submodel we evaluated was trait plasticity.
In the default configuration, all cohorts of a given plant functional type will have the same parameters, regardless of environmental conditions.
This ignores the globally-documented intraspecific trait variability as a function of light level [@niinemets_2010_review; @keenan_2016_global]. <!-- TODO Also, classical ecological succession theory bazzaz_1979_physiological? -->
In the alternate configuration, as light level decreases (trees become more shaded), specific leaf area increases and V~cmax~ decreases, following empirical relationships from the tropics [@lloyd_2010_optimisation].
